{\bf {\Large Evaluation and correction of noise related to physical processes in estimates of estuary metabolism}}

### 2014-08-18 assess.Rnw
started discussion, almost done...

The detided or normalized values for each regression were compared to the simulated data to evaluate the ability of weighted regression to reproduce the biological \ac{DO} signals. Results were summarized using Pearson correlation coefficients and the \ac{RMSE} between the predicted and observed \ac{DO} values and the detided and biological \ac{DO} values.  Overall, the weighted regressions provided accurate results for the detided time series compared to the `true' biological time series regardless of the simulation parameters (\cref{tab:dtd_perf1}) or window widths (\cref{tab:dtd_perf2}).  Mean correlation for all time series and window widths between the detided and biological values was \Sexpr{form_fun(perf_means['cor'])}, with values ranging from \Sexpr{form_fun(perf_rngs[1,'cor'])} to \Sexpr{form_fun(perf_rngs[2, 'cor'])}.  Mean error was \Sexpr{form_fun(perf_means['err'])}, with values ranging from \Sexpr{form_fun(perf_rngs[1,'err'])} to \Sexpr{form_fun(perf_rngs[2, 'err'])}.  Simulations with very poor performance (e.g., negative correlations) were those that had minimum widths for day windows and maximum widths for hour windows, or were those with the \ac{DO} signal composed entirely of noise from observation uncertainty. Conversely, simulations with detided time series that were identical to the true time series (e.g., correlation of one, \ac{RMSE} of zero) were those for which there was no biological or tidal influence.  While the latter examples do not represent real-world scenarios, they were included in the simulations to provide verification that the weighted regressoin provide reasonable results in extreme scenarios.

@@

The \ac{NERRS} is a federally-funded network of 28 protected estuaries established for long-term research, water-quality monitoring, education, and coastal stewardship \citep{Wenner04}.  Continuous water quality data have been collected at \ac{NERRS} sites since 1994 through the \ac{SWMP}.  In addition to providing a basis for trend evaluation, data from \ac{SWMP} provides an ideal opportunity to evaluate long-term variation in water quality parameters attributed to both biological and physical processes.  Continuous \ac{SWMP} data can be used to describe \ac{DO} variation at sites with different characteristics, including variation from ranges in tidal regime \citep{Sanger02} and rates of ecosystem production \citep{Caffrey03,Caffrey04}.

@@

Ecosystem metabolism was estimated from the \ac{DO} time series using the open-water technique \citep{Odum56} as described in \citet{Caffrey13}.  The method is used to infer net ecosystem metabolism using the mass balance equation:
\begin{equation}
\frac{\delta DO}{\delta t} = P - R + D
\end{equation}
where the change in \ac{DO} concentration ($\delta DO$, g O$_2$ m$^{-3}$) over time ($\delta t$, hours) is equal to photosynthetic rate ($P$, g O$_2$ m$^{-3}$ hr$^{-1}$) minus respiration rate ($R$, g O$_2$ m$^{-3}$ hr$^{-1}$), corrected for air-sea gas exchange at the interface ($D$, g O$_2$ m$^{-3}$ hr$^{-1}$) \citep{Caffrey13}. $D$ is estimated as the difference between the \ac{DO} saturation concentration and observed \ac{DO}, multiplied by a volumetric reaeration coefficient, $k_a$ \citep{Thebault08}.  The diffusion-corrected \ac{DO} flux estimates were averaged during day and night for each 24 hour period in the time series, where flux is an hourly rate of \ac{DO} change as the difference between observations at time $t$ and $t+1$.  Areal respiration rates were assumed constant during the night and substracted from daily gross production estimates to yield net ecosystem metabolism (\cref{tab:case_att}).

@@

\section{Effects of aggregation and importance of detiding}

A final point of concern is the period of observation within which observed \ac{DO} is affected by tidal height changes and the extent to which this affects the interpretation of ecosystem metabolism.  From a management or ecological perspective, daily estimates may not be a primary concern given that seasonal or annual rates may be more relevant for evaluating ecosystem dynamics with continuous monitoring data.  For example, \cref{tab:case_res} indicated that mean annual estimates of production and respiration were relatively unchanged for Rookery Bay and Sapelo Island, whereas \cref{fig:case_ex1,fig:case_ex2} indicates that substantial variation can occur on a daily basis for these sites.  Additionally, mean annual estimates for production and respiration were significantly different after detiding for Elkhorn Slough and Padilla Bay. Therefore, an evaluation of the effects of tidal variation on ecosystem metabolism for different lengths of observation is critical for understanding practical applications of weighted regression.  For example, what is the shortest period of observation for which mean metabolism estimates can be evaluated without inducing bias from tidal variation?

The observed and detided daily estimates were averaged by month and season (Fall,  Spring, Summer, and Winter) categories for each case study to evaluate the effects of different averaging periods on evaluating metabolism (\cref{fig:meta_sum1,fig:metab_sum2}).  Interestingly, estimates of net metabolism were generally similar regardless of aggregation categories for each case study.  This result suggests that averaged net metabolism estimates based on observed \ac{DO} time series will produce unbiased results at periods of observation as short as one month, although note that substantial within-month variability  may be observed compared to using a detided \ac{DO} time series.  However, significant variation in aggregated production and respiration estimates for month and season was observed for each case study.  Detided production and respiration estimates exhibited seasonal and monthly variation that was more characteristic of expected trends with increases in metabolism during warmer months.  For example, production estimates based on observed \ac{DO} were substantially muted for both Padilla Bay (\cref{fig:metab_sum1}) and Rookery Bay (\cref{fig:metab_sum2}) during summer months, whereas values were significantly higher based on the detided data. Results for Elkhorn Slough were an exception such that seasonal variation in production and respiration were significantly reduced after detiding.  Regardless of trends, these results suggest that the effects of tidal variation on daily metabolism estimates can affect interpretations of metabolic trends that are aggregated on longer time scales, particularly those as short as one month.

>>>>

The detided or normalized values for each regression were compared to the simulated data to evaluate the ability of weighted regression to reproduce the biological \ac{DO} signals. Results were summarized using Pearson correlation coefficients and the \ac{RMSE} between the detided time series and the biological \ac{DO} time series as a known component of the observed.  Overall, the weighted regressions provided accurate results for the detided time series compared to the `true' biological time series regardless of the simulation parameters (\cref{tab:dtd_perf1}) or window widths (\cref{tab:dtd_perf2}).  Mean correlation for all time series and window widths between the detided and biological values was \Sexpr{form_fun(perf_means['cor'])}, with values ranging from \Sexpr{form_fun(perf_rngs[1,'cor'])} to \Sexpr{form_fun(perf_rngs[2, 'cor'])}.  Mean error was \Sexpr{form_fun(perf_means['err'])}, with values ranging from \Sexpr{form_fun(perf_rngs[1,'err'])} to \Sexpr{form_fun(perf_rngs[2, 'err'])}.  Simulations with very poor performance (e.g., negative correlations) were those that had minimum widths for day windows and maximum widths for hour windows, or were those with the \ac{DO} signal composed entirely of noise from observation uncertainty. Conversely, simulations with detided time series that were identical to the true time series (e.g., correlation of one, \ac{RMSE} of zero) were those for which there was no biological or tidal influence.  While the latter examples do not represent real-world scenarios, they were included in the simulations to provide verification that the weighted regressoin provide reasonable results in extreme scenarios.

@@

\ac{NERRS} is a federally-funded network of 28 protected estuaries established for long-term research, water-quality monitoring, education, and coastal stewardship \citep{Wenner04}.  Continuous water quality data have been collected at \ac{NERRS} sites since 1994 through the \ac{SWMP}.  In addition to providing a basis for trend evaluation, data from \ac{SWMP} provides an ideal opportunity to evaluate long-term variation in water quality parameters attributed to both biological and physical processes.  Continuous \ac{SWMP} data can be used to describe \ac{DO} variation at sites with different characteristics, including variation from ranges in tidal regime \citep{Sanger02} and rates of ecosystem production \citep{Caffrey03,Caffrey04}.

@@

Ecosystem metabolism was estimated from the \ac{DO} time series using the open-water technique \citep{Odum56} as described in \citet{Caffrey13}.  The method is used to infer net ecosystem metabolism using the mass balance equation:
\begin{equation} \label{metrate}
\frac{\delta DO}{\delta t} = P - R + D
\end{equation}
where the change in \ac{DO} concentration ($\delta DO$, g O$_2$ m$^{-3}$) over time ($\delta t$, hours) is equal to photosynthetic rate ($P$, g O$_2$ m$^{-3}$ hr$^{-1}$) minus respiration rate ($R$, g O$_2$ m$^{-3}$ hr$^{-1}$), corrected for air-sea gas exchange at the interface ($D$, g O$_2$ m$^{-3}$ hr$^{-1}$) \citep{Caffrey13}. $D$ is estimated as the difference between the \ac{DO} saturation concentration and observed \ac{DO}, multiplied by a volumetric reaeration coefficient, $k_a$ \citep{Thebault08}.  The diffusion-corrected \ac{DO} flux estimates were averaged during day and night for each 24 hour period in the time series, where flux is an hourly rate of \ac{DO} change as the difference between observations at time $t$ and $t+1$.  Areal respiration rates were assumed constant during the night and substracted from daily gross production estimates to yield net ecosystem metabolism (\cref{tab:case_att}).

@@

\subsection{Effects of aggregation and importance of detiding}

A final point of concern is the period of observation within which observed \ac{DO} is affected by tidal height changes and the extent to which this affects the interpretation of ecosystem metabolism.  From a management or ecological perspective, the effects of tidal variatoin on daily estimates may not be a primary concern given that seasonal or annual rates may be more relevant for evaluating ecosystem dynamics with continuous monitoring data.  For example, \cref{tab:case_res} indicated that mean annual estimates of production and respiration were relatively unchanged for Rookery Bay and Sapelo Island, whereas \cref{fig:case_ex1,fig:case_ex2} indicates that substantial variation can occur on a daily basis for these sites.  The effects of tidal variation on estimates of ecosystem metabolism may not be a concern mean annual rates are the primary focus.  Conversely, production and respiration estimates were significantly different at both mean annual and daily time scales for Elkhorn Slough and Padilla Bay, suggesting caution in interpreting averages of metabolism estimates on longer time periods if observed \ac{DO} data are not detided. Regardless, an evaluation of the effects of tidal variation on ecosystem metabolism for different lengths of observation is critical for understanding practical applications of weighted regression.  For example, what is the shortest period of observation for which mean metabolism estimates can be evaluated if aggregation of observed data on longer time periods removes potential bias from detiding?

The observed and detided daily estimates were averaged by month and season (Fall, Spring, Summer, and Winter) for each case study to evaluate differences in mean metabolism estimates as a basis for evaluating aggregation effects on different periods of observation (\cref{fig:metab_sum1,fig:metab_sum2}).  Interestingly, estimates of net metabolism were similar regardless of the period of observation for which values were aggregated.  This suggests that averaged net metabolism estimates based on observed \ac{DO} time series will produce unbiased results at relatively short periods of observation (e.g., monthly), although note that substantial within-period variability may be observed compared to using a detided \ac{DO} time series.  However, significant variation in aggregated production and respiration estimates for month and season was observed for each case study.  Detided production and respiration estimates exhibited seasonal and monthly variation that was more characteristic of expected trends with increases in metabolism during warmer months.  For example, production estimates based on observed \ac{DO} were substantially muted for both Padilla Bay (\cref{fig:metab_sum1}) and Rookery Bay (\cref{fig:metab_sum2}) during summer months, whereas values were significantly higher based on the detided data. Results for Elkhorn Slough were an exception such that seasonal variation in production and respiration were significantly reduced after detiding.  Regardless of trends, these results suggest that tidal variation can affect interpretations of metabolic trends that are based on aggregations of daily values, particularly those as short as one month.

### 2014-08-18 discussion.Rnw
finished assessment section (two case figs, two metabolism summary figs, including explanation)
started discussion, almost done...

@@

@@

Although Sapelo Island had the largest reduction in anomalous metabolism estimates compared to the other sites (\cref{tab:case_res}), the example in \cref{fig:case_ex1} shows little change metabolism between time series for period of observations.  This example provides a potential explanation why detiding the \ac{DO} time series had variable effect on removing anomalous estimates between case studies.  Specifically, metabolism estimates in the ten day period were similar between the observed and detided values.  Metabolism is a daily integrated average of \ac{DO} flux such that variation from changes in tidal height on a semidiurnal period may be cancelled out by averaging on a 24 hour period.  Regardless, the detided \ac{DO} time series represents an unbiased estimate that more clearly represents variation from biological processes.

@@

why not just average, doesn't the noise get removed by aggregating reults over time?  Yes but make case that the method allows use of shorter time series to estimate metabolism - relate to nidzieko and pdbje

@@

effects of proc unc v obs unc

air-sea gas exchange, how might this influence results
\end{comment}

>>>>

The primary objective for development and application of the weighted regression technique was to provide a method for more accurately estimating ecosystem metabolism by removing bias associated with tidal change in observed \ac{DO} time series.  The application of weighted regression to simulated \ac{DO} time series with known characteristics and extension to continuous monitoring data from selected \ac{NERRS} sites provided a proof-of-concept that the method can isolate and remove variation in observed \ac{DO} from tidal change.  Moreover, production and respiration estimates using the detided \ac{DO} time series for Elkhorn Slough and Padilla Bay were significantly different than those using the observed data, particularly for aggregated time periods longer than one day. These results are particularly relevant given that previous estimates of annual means may not accurately reflect true metabolic signals if the effects of tidal variation confound biological signals in observed \ac{DO} time series.  Additionally, variation of mean estimates was substantially reduced for estimates based on detided \ac{DO} time series, suggesting that the certainty of conclusions from detided estimates can be improved even if the mean annual estimates do not change.  Monitoring data for periods of observation less than one year may also produce biased metabolism estimates if observed data are used.  Results for each case study showed that significant differences were observed for the detided data at seasonal and monthly aggregations, particularly during summer months for Padilla Bay and Rookery Bay.

Comparisons between detided and biological \ac{DO} time series from the simulations indicated that adequate results can be obtained from the weighted regression for a range of characteristics of \ac{DO} time series, as well as half window widths used in the regression.  An examination of scenarios that produced abnormal results can provide additional insight into factors that affect the performance of weighted regression.  For example, poor performance was observed when the observation uncertainty ($\epsilon_{obs}$) was high and both process uncertainty ($\epsilon_{pro}$) and tidal advection ($DO_{adv}$) were low.  These examples represent time series with excessive random variation, no auto-correlation, and no tidal influence.  Poor performance is expected because the weighted regression models a non-existent tidal signal in a very noisy \ac{DO} time series.  These results were observed even for time series with a large diel component of the biological \ac{DO} signal, suggesting that the model will produce unreliable results in microtidal systems with high noise and no serial correlation.  From a practical perspective, weighted regression should not be applied to noisy time series if there is not sufficient evidence to suggest the variation is related to tidal changes.  Similarly, results with perfect or near-perfect correlations between detided and biological \ac{DO} time series were observed when observation uncertainy and tidal advection effects were not in the simulated time series.  Although there is no logical basis for applying weighted regression to such a time series, the results will not be misleading, as was the case for low tidal advection, high observation uncertainty, and low process uncertainty.

The performance metrics used to evaluate weighted regression with the case studies indicated that detiding improved estimates of ecosystem metabolism.  Correlations of metabolism estimates with tidal height changes suggested that detiding produced less biased estimates, although trends were not particularly clear as correlations were reduced in some cases (Sapelo Island) or reversed in others (Padilla Bay).  However, correlations of net metabolism estimates were reduced in all cases.  Tidal height changes directly affect the measured rate of change of oxygen, which is an integrated measure of both production and respiration (\cref{metrate}).  An evaluation of tidal height change with production or respiration may be misleading since each represents a unique portion of the diel \aC{DO} signal that is directly affected by tidal variation.  Regardless, the proportion of anomalous metabolism estimates was reduced by detiding for all case studies, although this measure may also be an incomplete indication of the combined effects of tidal variation.  Negative production and positive respiration estimates suggest assumptions of the open-water method are violated \citep{Needoba12}.  However, `normal' estimates (positive production and negative respiration) may still include a significant source of bias from physical advection by providing over-estimates of true values.  \citet{Nidzieko14} observed that net metabolism at Elkhorn Slough was more often heterotrophic during maximum spring tides that occurred at nighttime, as a substantially larger area of salt marsh was inundated leading to higher respiration estimates.  Although this result supports our general conclusions, a broader discusion regarding whether or not this represents a bias in metabolism from physical advection may be needed.

A strength of the weighted regression approach is the lack of assumptions that are required for relationships between \ac{DO} and tidal variation over time.

% emphasis on improvement over other methods

% new insights, reinterpretation of existing data

@@

- degree to which method meets need defined in introduction
  -sims
  -case studies

- potential for new insight
- whether existing data should be reinterpreted
  -potentially

@@

 Assumptions of relationships between variables are not necessary using this adaptive weighting scheme given that the method has the ability to interpret statistical relationships without prior knowledge.

@@

@@

air-sea gas exchange, how might this influence results

Most bias may be expected during the summer...
\end{comment}

### 2014-08-18 intro.Rnw
started discussion, almost done...

This article describes use of a novel method for quantifying and removing noise in estimates of ecosystem metabolim for estuaries.  Specifically, we characterize the effects of tidal advection on \ac{DO} observations to improve estimates of open-water metabolism with multi-year time series of high frequency ($<$ one hour) water quality data.  The focus of our analysis is the use of a weighted regression method previously developed for trend analysis of pollutant concentrations in streams and rivers \citep{Hirsch10}.  A weighted regression approach is applied to create dynamic predictions of \ac{DO} as a function of time and tidal height change, which is then used to normalize, or detide, the \ac{DO} signal.  The analysis is presented in two steps.  First, we apply a simulation approach to create time series of \ac{DO} observations with known characteristics to evaluate ability of the weighted regression to predict the time series and remove the effects of tidal advection.  Second, four case studies of multi-year time series are used to further explore use of the weighted regression approach to remove potential noise in \ac{DO} signals from tidal advection.  Comparisons of observed and detided \ac{DO} values are compared, in addition to estimates of open-water metabolism before and after detiding of the \ac{DO} time series.  Overall, the analysis provides a means to improve certainty in conclusions from observed \ac{DO} for evaluating the relative roles of biological and physical processes in estuarine systems.  Applications of the weighted regression approach are expected to have wide-ranging implications for management and ecosystem monitoring by outlining strategies for obtaining water quality estimates with more accuracy.

>>>>

This article describes the theory and application of a novel method for detiding an observed \ac{DO} time series for the purpose of removing biases from tidal variation in estimates of ecosystem metabolim for estuaries.  Specifically, the method characterizes the effects of tidal advection on \ac{DO} observations to improve estimates of open-water metabolism with multi-year time series of high frequency ($<$ one hour) water quality data.  The focus of our analysis is the use of a weighted regression method previously developed for trend analysis of pollutant concentrations in streams and rivers \citep{Hirsch10} and recently adapted to improve trend evaluation of water quality parameters in estuaries \citepalias{BeckIR}.  A weighted regression approach is applied to create dynamic predictions of \ac{DO} as a function of time and tidal height change, which is then used to normalize, or detide, the \ac{DO} signal.  The analysis is presented in two steps.  First, we apply a simulation approach to create time series of \ac{DO} observations with known characteristics to evaluate ability of the weighted regression to remove the effects of tidal advection.  Second, four case studies from the \aclu{NERRS} (\acs{NERRS}, \citealt{Wenner04}) are used to further validate the use of weighted regression to remove potential noise from tidal advection in estimates of ecosystem metabolism.  Estimates of open-water metabolism before and after detiding of the \ac{DO} time series for each case study.  Overall, the analysis is meant to provide a means of improving certainty in conclusions from observed \ac{DO} for evaluating the relative roles of biological and physical processes in estuarine systems.  Applications of the approach are expected to have wide-ranging implications for management and ecosystem monitoring by outlining strategies for interpreting water quality data with more accuracy.

### 2014-08-18 swmp_noise.tex
started discussion, almost done...

% aliased citations
\defcitealias{CDMO14}{CDMO 2014}
\defcitealias{RDCT14}{RDCT 2014}

@@

The detided or normalized values for each regression were compared to the simulated data to evaluate the ability of weighted regression to reproduce the biological \ac{DO} signals. Results were summarized using Pearson correlation coefficients and the \ac{RMSE} between the predicted and observed \ac{DO} values and the detided and biological \ac{DO} values.  Overall, the weighted regressions provided accurate results for the detided time series compared to the `true' biological time series regardless of the simulation parameters (\cref{tab:dtd_perf1}) or window widths (\cref{tab:dtd_perf2}).  Mean correlation for all time series and window widths between the detided and biological values was 0.56, with values ranging from -0.78 to 1.00.  Mean error was 1.27, with values ranging from 0.00 to 2.47.  Simulations with very poor performance (e.g., negative correlations) were those that had minimum widths for day windows and maximum widths for hour windows, or were those with the \ac{DO} signal composed entirely of noise from observation uncertainty. Conversely, simulations with detided time series that were identical to the true time series (e.g., correlation of one, \ac{RMSE} of zero) were those for which there was no biological or tidal influence.  While the latter examples do not represent real-world scenarios, they were included in the simulations to provide verification that the weighted regressoin provide reasonable results in extreme scenarios.

@@

@@

Although Sapelo Island had the largest reduction in anomalous metabolism estimates compared to the other sites (\cref{tab:case_res}), the example in \cref{fig:case_ex1} shows little change metabolism between time series for period of observations.  This example provides a potential explanation why detiding the \ac{DO} time series had variable effect on removing anomalous estimates between case studies.  Specifically, metabolism estimates in the ten day period were similar between the observed and detided values.  Metabolism is a daily integrated average of \ac{DO} flux such that variation from changes in tidal height on a semidiurnal period may be cancelled out by averaging on a 24 hour period.  Regardless, the detided \ac{DO} time series represents an unbiased estimate that more clearly represents variation from biological processes.

@@

effects of proc unc v obs unc

@@

% comment about performance of simulations, window width is a more critical issue
An examination of unique scenarios can provide insight into factors that affect the ability of weighted regression to resolve variation in observed \ac{DO} from tidal effects ($DO_{tid}$, \cref{fig:do_dtd}) and the mean response of \ac{DO} given constant tidal height ($DO_{nrm}$, \cref{fig:do_dtd}).  These unique sources of variation are represented by $DO_{bio}$ and $DO_{adv}$ as additive components of $DO_{obs}$ (\cref{do_obs}).  Although comparison of \cref{fig:err_surf1} and \cref{fig:err_surf2}) suggested that characteristics of the \ac{DO} time series had a larger influence on  model performance than window widths, examples where model fit was either very good or very poor were time series with extreme characteristics.  For example, poor performance was observed when the observation uncertainty ($\epsilon_{obs}$) was high and both process uncertainty ($\epsilon_{pro}) and tidal advection ($DO_{adv}$) were low.  These examples represent time series with excessive random variation, no auto-correlation, and no tidal influence.  Poor model performance is expected because the weighted regression attempts to isolate variation from a non-existent tidal signal in a very noisy \ac{DO} time series.  From a practical perspective, the weighted regression should not be applied to such a time series. Most of the simulations evaluated provided a reasonable reprsentation

@@

>>>>

% aliased citations
\defcitealias{BeckIR}{Beck and Hagy, In review}
\defcitealias{CDMO14}{CDMO 2014}
\defcitealias{RDCT14}{RDCT 2014}

@@

The detided or normalized values for each regression were compared to the simulated data to evaluate the ability of weighted regression to reproduce the biological \ac{DO} signals. Results were summarized using Pearson correlation coefficients and the \ac{RMSE} between the detided time series and the biological \ac{DO} time series as a known component of the observed.  Overall, the weighted regressions provided accurate results for the detided time series compared to the `true' biological time series regardless of the simulation parameters (\cref{tab:dtd_perf1}) or window widths (\cref{tab:dtd_perf2}).  Mean correlation for all time series and window widths between the detided and biological values was 0.56, with values ranging from -0.78 to 1.00.  Mean error was 1.27, with values ranging from 0.00 to 2.47.  Simulations with very poor performance (e.g., negative correlations) were those that had minimum widths for day windows and maximum widths for hour windows, or were those with the \ac{DO} signal composed entirely of noise from observation uncertainty. Conversely, simulations with detided time series that were identical to the true time series (e.g., correlation of one, \ac{RMSE} of zero) were those for which there was no biological or tidal influence.  While the latter examples do not represent real-world scenarios, they were included in the simulations to provide verification that the weighted regressoin provide reasonable results in extreme scenarios.

@@

The primary objective for development and application of the weighted regression technique was to provide a method for more accurately estimating ecosystem metabolism by removing bias associated with tidal change in observed \ac{DO} time series.  The application of weighted regression to simulated \ac{DO} time series with known characteristics and extension to continuous monitoring data from selected \ac{NERRS} sites provided a proof-of-concept that the method can isolate and remove variation in observed \ac{DO} from tidal change.  Moreover, production and respiration estimates using the detided \ac{DO} time series for Elkhorn Slough and Padilla Bay were significantly different than those using the observed data, particularly for aggregated time periods longer than one day. These results are particularly relevant given that previous estimates of annual means may not accurately reflect true metabolic signals if the effects of tidal variation confound biological signals in observed \ac{DO} time series.  Additionally, variation of mean estimates was substantially reduced for estimates based on detided \ac{DO} time series, suggesting that the certainty of conclusions from detided estimates can be improved even if the mean annual estimates do not change.  Monitoring data for periods of observation less than one year may also produce biased metabolism estimates if observed data are used.  Results for each case study showed that significant differences were observed for the detided data at seasonal and monthly aggregations, particularly during summer months for Padilla Bay and Rookery Bay.

Comparisons between detided and biological \ac{DO} time series from the simulations indicated that adequate results can be obtained from the weighted regression for a range of characteristics of \ac{DO} time series, as well as half window widths used in the regression.  An examination of scenarios that produced abnormal results can provide additional insight into factors that affect the performance of weighted regression.  For example, poor performance was observed when the observation uncertainty ($\epsilon_{obs}$) was high and both process uncertainty ($\epsilon_{pro}$) and tidal advection ($DO_{adv}$) were low.  These examples represent time series with excessive random variation, no auto-correlation, and no tidal influence.  Poor performance is expected because the weighted regression models a non-existent tidal signal in a very noisy \ac{DO} time series.  These results were observed even for time series with a large diel component of the biological \ac{DO} signal, suggesting that the model will produce unreliable results in microtidal systems with high noise and no serial correlation.  From a practical perspective, weighted regression should not be applied to noisy time series if there not sufficient evidence to believe the variation is related to tidal changes.  Similarly, results with perfect or near-perfect correlations between detided and biological \ac{DO} time series were observed when observation uncertainy and tidal advection effects were not in the simulated time series.  Although there is no logical basis for applying weighted regression to such a time series, the results will not be misleading, as was the case for low tidal advection, high observation uncertainty, and low process uncertainty.

The performance metrics used to evaluate weighted regression with the case studies indicated that detiding improved estimates of ecosystem metabolism.  Correlations of metabolism estimates with tidal height changes suggested that detiding produced less biased estimates, although trends were not particularly clear as correlations were reduced in some cases (Sapelo Island) or reversed in others (Padilla Bay).  However, correlations of net metabolism estimates were reduced in all cases.  Tidal height changes directly affect the measured rate of change of oxygen, which is an integrated measure of both production and respiration (\cref{metrate}).  An evaluation of tidal height change with production or respiration may be misleading since each represents a unique portion of the diel \aC{DO} signal that is directly affected by tidal variation.  Regardless, the proportion of anomalous metabolism estimates was reduced by detiding for all case studies, although this measure may also be an incomplete indication of the combined effects of tidal variation.  Negative production and positive respiration estimates suggest assumptions of the open-water method are violated \citep{Needoba12}.  However, `normal' estimates (positive production and negative respiration) may still include a significant source of bias from physical advection by providing over-estimates of true values.  \citet{Nidzieko14} observed that net metabolism at Elkhorn Slough was more often heterotrophic during maximum spring tides that occurred at nighttime, as a substantially larger area of salt marsh was inundated leading to higher respiration estimates.  Although this result supports our general conclusions, a broader discusion regarding whether or not this represents a bias in metabolism from physical advection may be needed.

A strength of the weighted regression approach is the lack of assumptions that are required for relationships between \ac{DO} and tidal variation over time.

% emphasis on improvement over other methods

% new insights, reinterpretation of existing data

@@

@@

@@

@@

To date, only a few analyses have focused on systematic comparisons of estuarine metabolism estimates across broad spatial and temporal scales.  Exceptions include \citet{Caffrey03}, \citet{Caffrey04}, and \citet{Caffrey13}.
